Details matter: Similar-looking host galaxies can produce different merging compact binary populations

### 2015-04-23 paper/paper.tex
wrote some galaxy descriptions.

Figure \ref{fig:TwoGalaxies} shows the history of

>>>>

{\bf Richard go ahead and edit this however is needed.}  The evolution
of a galaxy, in terms of its stellar mass and metallicity evolution,
depends strongly on its interaction history.  Galaxies which look
similar at the present day may have had drastically different
histories, which may result in differences in compact object merger
rates.  To investigate whether galaxy history affects the GRB event
rate, we have chosen two simulations which are extremely similar at $z
= 0$ but differ strongly in their merger histories.

The simulation h277 (Boring Galaxy) is a Milky Way analog with a
quiescent merger history.  It experiences its last major merger at $z
= 3$, after which a small number of minor interactions permeate its
life.  This simulation has been shown to emulate several Milky Way
properties, including stellar dynamics
\citep{Loebman12,Loebman14,Kassin14}, baryon fraction
\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10), and
  disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir}
  = 6.79 \times 10^{11}$ \msun, stellar mass $M_* = 4.24 \times
  10^{10}$ \msun, and circular velocity $v_{circ} = xx$ km s$^{-1}$.

  The simulation h258 (Exciting Galaxy), on the other hand, has a much
  more active merger history.  At $z = 1$ there is a 1:1 merger event;
  a gas disk rapidly reforms following the collision (see
  \citet{Governato09}), resulting in a massive disk galaxy at $z = 0$
  which looks remarkably similar to the Milky Way and to the other
  simulation, h277.  Prior to the $z = 1$ merger, each of the two
  progenitor galaxies actually experiences its own additional major
  merger events around $z = 2.5$ ({\bf check!}).  The combination of
  the series of major mergers, plus a number of minor interactions and
  flybys, gives a stark contrast to the relatively quiescent history
  of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
  \times 10^{11}$ \msun, stellar mass $M_* = 4.46 \times 10^{10}$
  \msun, and circular velocity $v_{circ} = xx$ km s$^{-1}$.

  Due to the differences in merger histories, the metallicity
  evolution of h258 and h277 also differ at early times.  Figure
  \ref{fig:TwoGalaxies} shows the history of the mean metallicty of
  recently formed stars vs time (thick solid lines), where we define
  recent as within the past 50 Myr.  The shaded regions correspond to
  one standard devation of the mean, while the thick dashed lines
  represent the top and bottom 90\%.  We see that {\bf different things happen at different times.}
